Constraint Programming - Inside Gecode

### 2014-05-04 paper.tex
restart strategies

	\subsubsection{Branch-and-Bound Search}
	Branch-and-bound refers actually to two parts, a Branch-and-reduce search and bounding. Branch-and-reduce itself is the continous constraint propagation to reduce the variable domains combined with branching when there is no further reduction by constraint propagation possible. A simple heuristic for branching would be to split the biggest domain into two equal sized intervals.
	Bounding is then the step which transforms the Branch-and-reduce search into an optimization. To be able to do this an objective function is necessary. In the following I will assume that the objective function has to be minimized with a loss of generality.
	Every Branch splits the total problem into two sub problems. With some additional constraints, for example one variable must be an integer $x \in \mathbb{Z}$, it may happen that the real optimum of a sub problem is not the same one as if this additional constraint is considered. For finding the first optimum the trick is to branch in ways that a certain sub problem ends up with only a few possible candidates left, which then can be tested each. With this first optimum the search algorithm has then a so far best optimum which can be used as upper bound for the optimum. If for one sub problem the relaxed optimum, the optimum without for example the constraint of integrity, is worse than this upper bound the sub problem can be pruned. Only if the relaxed optimum turns out to be better than the best optimum so far it is necessary to look further into this sub problem and either test the left candidates or apply additional branching.

@@

	\subsubsection{Restart Strategies}

>>>>

	\subsubsection{Branch-and-Bound Search}
	Branch-and-bound refers actually to two parts, a Branch-and-reduce search and bounding. Branch-and-reduce itself is the continous constraint propagation to reduce the variable domains combined with branching when there is no further reduction by constraint propagation possible. A simple heuristic for branching would be to split the biggest domain into two equal sized intervals.

	Bounding is then the part which transforms the Branch-and-reduce search into an optimization. To be able to do this an objective function is necessary. In the following I will assume that the objective function has to be minimized with a loss of generality.

	Every Branch splits the total problem into two sub problems. With some additional constraints, for example one variable must be an integer $x \in \mathbb{Z}$, it may happen that the real optimum of a sub problem is not the same one as if this additional constraint is considered. For finding the first optimum the trick is to branch in ways that a certain sub problem ends up with only a few possible candidates left, which then can be tested each. With this first optimum the search algorithm has then a so far best optimum which can be used as upper bound for the optimum. If for one sub problem the relaxed optimum, the optimum without for example the constraint of integrity, is worse than this upper bound the sub problem can be pruned. Only if the relaxed optimum turns out to be better than the best optimum so far it is necessary to look further into this sub problem and either test the left candidates or apply additional branching.

@@

	\subsubsection{Restart Strategies}
	Branching means always to apply certain heuristics and this heuristics may fail or produce bad results for the first execution. If it turns out that the search tree is build in a disadvantageous way a restart strategy may do the trick to improve the search. For such a restart the heuristic is improved, based on the things the search has learned to be a not so good solution during the first or first few attempts to build a search tree.
	For practical application several variants of restart strategies were proposed \cite[p.~113]{handbookCP}
